\section{Sample Data} % (fold)
\label{app:sample_data}
	\begin{center}
		\begin{footnotesize}
		\begin{longtable}{cp{3.8in}c}
			\label{tab:sample_data}\\
			\caption{\normalsize Sample Data}\\
			\toprule
			\multicolumn{1}{c}{Index} &
			\multicolumn{1}{c}{Message} &
			\multicolumn{1}{c}{Actual Sentiment}\\
			\toprule
			\endfirsthead

			\multicolumn{3}{c}{{\bfseries \tablename\ \thetable{} -- continued from previous page}}\\
			\toprule
			\multicolumn{1}{c}{Index} &
			\multicolumn{1}{c}{Message} &
			\multicolumn{1}{c}{Actual Sentiment}\\
			\toprule
			\endhead

			\bottomrule
			\multicolumn{3}{c}{{Continued on next page}} \\
			\bottomrule
			\endfoot

			\bottomrule\bottomrule
			\endlastfoot

1 & hey, still on for monday night study session, just facebook or call about what time you think you'll be here so we can let you oin and come on up. if your calling my extension is 7154. can't wait to study...yeah! not. & neutral\\
2 & hey what is your name on twitter? & neutral\\
3 & Hey!  We will be at Ocean Walk.  It is on Mallory near the village. & neutral\\
4 & This is funny. & positive\\
5 & My goal is to not be tired. Ahahah.   & neutral\\
6 & Yes. Let's! Hannah needs to be there around 11 ... is Liam on earlier? I figure we could leave around 9 and hang for the day ... what do you think? & positive\\
7 & Thanks - How is the not smoking going? & positive\\
8 & "Os Burn" is looking for you.  heh & neutral\\
9 & Hey.... my long lost sister...I'm happy you found me,how is everything? & positive\\
10 & question for you...since you are involved in 2009 POTK...I am hopeful you can help. Katey was upset b/c she and Katlynn Hansen were both told that they would not be performing or sitting with the rest of the 5th grade?  In the past, performances were arranged by grade, they said they are performing after the third grade, but before the fourth, and sitting on the opposite side of the auditorium.  I am not the parent volunteer for this group, Jamie Hansen is, but she has not heard back from Bobbie or Stan, and asked me to intervene.  They are scheduled to perform before intermission. Any idea what is going on...THANKS!! & negative\\
11 & Happy Birthday, girl!  Hope it is a great day for you! & positive\\
12 & that bumper sticker is so crazy cause we were literally just talking about that today!! & positive\\
13 & ohhhh and it's BOYS BEFORE FLOWERS. get it right! maica is getting into it:) you're my next target..heheh & positive\\
14 & do u and clark want a boy or girl ! I think health is just perfect lol & positive\\
15 & HEY DANIELLE!!!!!! I already miss ya girl!! Hope all is well!!! Let's keep in touch!!!! & positive\\
16 & Burnt like sunburned biotch!!!!lol & negative\\
17 & I've been asked many times where I caught that fish and the reply is always the same.  THE LOWER LIP!!! & neutral\\
18 & Hhhhmmmmm, smells like a bachelorette party is on the horizon! You deserve it honey.;))) & positive\\
19 & Time means nothing when u never ever win. Economy's rough i blame bush for that not the pens fault and ya lemieux is the fuckin man so dont hate him for being the best with money & positive\\
20 & I always knew Juan and you will end up together!  You both look good!  I am well and have two wonderful babies.  Eric and I separated years ago after Germany and I settled in Alexandria, VA with my sister.  I remarried in 2005 and here I am...I am very happy!  We have so much to talk about.  Hope all is well with you and let me know what's up. & positive\\
21 & Hey, duh, I was just getting ready for tomorrow, not thinking about our lesson day. Since it is Easter, and I have a lot planned and a lot to do tomorrow, can we skip this weeks lesson? You said you werent gonna give me anything new anyway, so. Thanks! :) & negative\\
22 & Hi!  I would LOVE to - but tomorrow night isn't good for me (I have too much to do in this house that I have been totally neglecting) - next week would be great!!!! How about Monday, Tuesday, Wed or THursday night (next Friday is Good Friday and I don't feel right about having a few that night!).  Let me know which night is good for you.  I will make sure I go to the bank before we go so I'm not locked in the bank at night - that was so funny!  Let me know - I can't wait! & negative\\
23 & where dya dig up those photos from haha they made me laugh,  cant believe wa we look like in the one cor tha purple top im wearing.  even more cringe i liked it once cos i can remember it. ive always dressed to get notice (:  & positive\\
24 & U should be!  Haha.  She sees me 24/7 u get like 12 hours a week & neutral\\
25 & haha i know=) omg ur speakin frenglish too!xD was yellow flirtin wit another guy? wouldnt surprise me it seems like she flirts with anythin that moves :P and  i <3 ZACCCC toooo hes THE man & positive\\
26 & Don’t forget Georgia State’s Relay for Life is tomorrow (Friday April 3) at Panthersville Field! The fun kicks off at 7 pm and goes until 7 am Saturday morning! Panther Busses are leaving the Commons every 30 minutes beginning at 6pm! If you want food and a t-shirt the entry fee is \$10, if you aren’t interested in eating and sporting a super awesome shirt then it’s free. Bring some \$1s in case there is something wonderful that you want to buy. All the money goes directly to the American Cancer Society in order to fund important cancer research! Bring all your friends!! & positive\\
27 & Good morning Robbie boy,just thought i'd write you something and tell you that the sun is shining here in Hamburg.You should let me know when you're home again so i can get intouch.I spoke to Dutch and he isnt not doing super by the sound of things.So i'm signing off here and you take care buddy. & positive\\
28 & Change isnt not always good! & positive\\
29 & Happy birthday g wit yo old ass i try 2 call u lata on the phone 2 say it ovea the phone 2 but if i dont you no u is my g fa life. & positive\\
30 & i go 24 but i go at 6am after work. thats like the only time i have for gym. & neutral\\
31 & collette....lolz! ; p ELLO! leelee here and she said hiiiiiiiiii, oh jen if ur makoin she said to tell u hi too..lolz. eeek, the boredom is killing me...hmph! am i the only one who can be bored at 12:30 in the morning? lol..... oh wellie, ttyl, or whenever u decide to GET A PHONE! anyhoo, check ya l8r dudette...*hugz* ;..; <vampy the vampire... & positive\\
32 & no because everyday is a new year & neutral\\
33 & he trained in korea and japan and is reasonably priced & neutral\\
34 & weyes it is a big step but i cant think of anything else can you? & neutral\\
35 & MARLA!!!! happy freaking birthday i hope it is the best god damn 21st birthday in the history of 21st! & positive\\
36 & Home is good bro, hope your having a swell easter break :) & positive\\
37 & i hope you dont hate it. i will send u my \# & positive\\
38 & hey dude. not alot just partying now. I know why dont you come school you poof? school is homo anyways so be glad you dont go there ! Im always a good girl. take care ok mate & postive\\
39 & Yeah!  Tiffani is so grown up now!!!  She didn't remember me, though :-(  Guess that means we have to get together soon so she can see me face from time to time haha & negative\\
40 & Hi hun im fine thanks bump is getting bigger, 19 weeks tommorow yeh! one week to go to find out boy or girl well hopefully aslong as legs arnt crossed!! ha ha thankyou for keeping some stuff for me that will be great everything helps, hope you are well and little dylan xxx & positive\\
41 & Hi Logan, I got your note, and I know- that is the only picture that I can upload on this facebook! YES, we want you to babysit anytime!!!!!!!! I will see you Sunday....Love you, Potka & positive\\
42 & OK so I just sent you a drink thingy from that app thingy and the only beer or whiskey they have some some green lucky shit. So I figured what the hell!! LOL Hope all is well! & positive\\
43 & I was just kidding!! She is a good photog!! I saw her at the boys party....she is a good girl! Nothing planned just want to spend time with my boys!! & positive\\
44 & Hey Neice, Hope that you had a very Happy Birthday yesterday. How is Ali doing after her surgery? & positive\\
45 & My finger is feeling better, Doc says I am a fast healer. & positive\\
46 & Hey, thanks!  Dani and I were in Logan last weekend, so it woulda been kinda difficult to meet up here.  We went for my b-day and Easter, and to start looking for apartments.  We wer accepted to USU.  I feel lame for not telling you that earlier.  We'll be moving up there at the beginning of next month, right after I graduate from Snow.  BTW, my phone \# is (435)610-0085, and Dani's is (435)881-2106.  Also, I love the little thing you have in your "About Me" box.  It's pretty much true, except you never really drove me crazy.  Anywho, I gotta get to bed so's I can get up for classes tomorrow.  Love ya, Ashley!  See you 'round! & positive\\
47 & hah and yeah dude same. i just wanna get out of schl lol. & neutral\\
48 & Yeah it seems like it will all work out.  SO the middle east, where are you going and why...? & neutral\\
49 & i been chillin...playing semi pro bball in europe...cant complain...bout to come home for summmer...first time being back in like two years!!! & neutral\\
50 & oh yeah North Asheboro park! bring som sour patch kids, boom box, and LPS! we will have a ball....and we can NOT forget the camera to take millions of pics! i miss L.E.M...all those damn pic we took together!  & positive\\
51 & when I get home i hope you kidnap me for a while! I will just stay with you at your place like old times! :) & positive\\
52 & lol thanks you know ima awesome like that. I went to the gulf of mexico. What about u? & positive\\
53 & Hi huni i hope you went to see the doc like you sed u would xx & neutral\\
54 & Not much is new up here.  The grass is getting greener and the sun is getting higher, so that is great...other than that, things are finally fun up here and PT is getting along pretty well. & positive\\
55 & I am done in like two weeks (soooooo weird to say), so I'll be over soon, haha.   & neutral\\
56 & my cenie et cema!!! how long will you two be in paris? it's so bad we can't be together now...I am doing great! trying to write my thesis - which is not really working out right now :-) but I'm enjoying the beautiful spring weather...what are your travel plans for this year? big big bisous and hug to you and cema!!! I miss you!!!! love* & positive\\
57 & Hi Karen!  Miss you too!!!  Eliza's party was really good!  I'll have to post some pics!  I am not sure where I've been...lol!  Seems like since her bday, things have been nuts.  I see you got a job!  You go girl!  How is it?  I'm so happy for you!  I hope we get to talk soon! & positive\\
58 & Not stalking you, just keep track of my friends and what is going on with them. Shall I remove you from "friend"status, oh evil one? Look at all of these females.....hmmmmmmmmmmmmmmm............wonder why you have problems with women......................... :-) & negative\\
59 & seems like uts just allergies...have to get tylenol i guess.   but glad to hear your all doing well.  i'm with you on the spring thing...of course...we do need the rain here in nj...so i guess it's good too...i'll take it as i can right now...will dread the extreme heat of the summer. & negative\\
60 & your moustache is pretty disgusting. & negative\\
61 & how is albany? & neutral\\
62 & y do u guys alwayz hav  to wrte in spanish is it a creat or somthin & negative\\
63 & I DID find my Fleming book. I wonder what is incorrect in it and why. It was done nearly 40 years ago so I would think a nice history would be due. Hum, will have to think about that. Arcadia printings would be \$20...think enough Erie people would pay that?:) & negative\\
64 & This is such a cold and dark Easter....think I will curl up with a book with what is left of the day.....c & negative\\
65 & heyy no worries yeah good how bout yours what you get up to?  & positive\\
66 & I hope you had a super birthday!  It is hard to believe that we are only 25! & positive\\
67 & Fuck that. Waterproof wear is FOR THE WEAK!  & positive\\
68 & haha. no no. its all good i like stories. haha. omg. nicee. we went to the verizon thing too. where you swiped the card. and i think there might've been one at like the saturn car place where they had you swipe the card too. got nothing. boo. but w/e but 10th row center nicee! i was 17th row center, we sat outside the day the tickets went on sale in the like below zero weather, and froze our butts off, it was crazy, but worth it especially for my sister, b/c her and her 2 friends got fourth row right in front of kevin. i was so mad at her, but w/e. it was a fun concert anyways. lol. and we have lower bowl somewhere for taylors. i think section 107? but yeah. its van andel, and every seat there is pretty decent so i'm not complaining. and yeah.. i'll let you in on a secret.. mike mannign was asking one of my friends about van andel and if its nice and stuff, b/c he said they're going to be doing an arena tour soon... so idk. but shh. keep it on the DL. haha. and i know what you mean, & negative\\
69 & haha yea even my 2nd sister (joyce) is taller! but everyone is fine here, at least the last time i saw them haha. my brother and older sister have their own place now, so i dont see them every day. & neutral\\
70 & Hi there! You so have to stop by and see us at the Y when you get back. Graduation is May 29th. 6:00 I think. & positive\\
71 & It has been. When ya coming back? (Lol). We sure miss you girl.  Love that picture too, you look like a model!  Love you, stay in touch & positive\\
72 & Wow!  Hi Michelle!!  I am so happy to see that God is blessing you!  It is a wonderful thing when God becomes \#1 in a persons life!  You have always been such a beautiful woman, but with Gods light you shine even more!   & positive\\
73 & no thank you.  your family is so awesome.  it was so much fun. i'd love to do it again.  thanks for all your listening and advice.  you're wonderful! & positive\\
74 & H'okay, soooo the museum is the Bellevue Arts Museum. I'll get you at Interlake at 2:30, yes? And then we can take the 230 straight there. & neutral\\
75 & No, I only have four kids...the one next to my oldest daughter is my son in law!  Thanks Grace, great to hear from you too. & positive\\
76 & You little wild woman you!  I miss you!  When are you coming to visit?  How is your mom?  I am getting ready to pay for my next cruise.  We are going with a group of people we cruised with in December.  There were about 14 of us.  We are all signing up for January 2010.  So far there are 10 of us and growing.  Some of my kids are going.  Can you believe Jared is going to be a daddy?  Ouch.  Daniel made me a grandma last year in July.  She (Madison Haleigh Bishop) is absolutely gorgeous.  I love her to death.  She really little (petite) but already getting ready to walk.  She can say bubble, dada, and of course, mama.  I just want to pinch her to make sure she's real.  She is so cute.  You need to look at all of her pics on my facebook.  Grandma is crazy about her.  Come see us very soon.  val & positive\\
77 & Hi Camille -yes Ava will be 18 months starting very soon - even her size 2 shoes are getting tight now - she is so chubby!  LOL.  By the way, can you confirm for me exactly how hold your girls are?  Looking forward to seeing you guys - Sue cant make it - Lee called me - she has a long recovery ahead of her apparently. & neutral\\
78 & Hiya sis....im getting a new setee nmext week so you can have mine if you want...iv just had it cleaned so its like new...let me know if you want it lvya xxxx & positive\\
79 & leonaaaaaaard...how r u?i m sure u doing great..how is life in singapore..i m leaving today...going to india..cu...bye & positive\\
80 & Tue 9, Wed 330, Thr 8, Fri closed  I thought you needed a Mon session ? If so 8 is fine. You ready for me to film again? :) I want to get some outside shots too - bosus with golf swing, med ball, etc & positive\\
81 & hahahha yea i no the feeling ughh this weather i feel so sick i need a nap big time but i dun feel lik goin to sleep :( & negative\\
82 & haha yeah i was lookin at them this morning and didnt realise how & neutral\\
83 & Dude like i said there was a miniseries before the acual show started. Like 4 two hour episode i think. I have no idea where you can find those though. & neutral\\
84 & na social work as my major doin a double degree! social work is great! i work as a kindy teacher i love it! its great fun!! love all my kids i wana take them home... haha na havnt been 2 perth yet but yeah will at the end of the semester xox & positive\\
85 & Evansville is not a nice city, Ive played music there lots of times. & negative\\
86 & I like da pics u look fresh & positive\\
87 & You like the tuxedo cats, too. She's a tiny one - only 7 pounds. & positive\\
88 & hey girlie...i sent you a txt but no reply so I will try on here.  I just found out that wed the girls track team is going to the y to help with the healthy kids day there.  It isn't over till 6..do you want to reschedule kels or have her come when she is done?  She could come thurs nite after 5:30, whatever works for you! & neutral\\
89 & I make the boys birdsnest all the time. They love them. What I don't make them is orange potatoes and sausage. YUCK!!! & negative\\
90 & hahah and remmeber how i needed a wrt 200 syllabus well i just like emailed the english department demanding someone send me one hahah & neutral\\
91 & sweet! thanks darling! ill see you on friday then...i may give you a ring before though like probably before im leaving or somehting...x & positive\\
92 & I've heared that Qatar is a nice country, is that true? I did never ever visit sny arab country but Irag to see one of the seven wonders which id Hanging Babel Garden in 1980. although i visit all of Europe, Canda and finally I do live in Usa.please send me some pictures for Qatar. have a great day. & neutral\\
93 & thank you very much Janie.  The body may still be there... but the mind is fading fast.. & negative\\
94 & How is de baby, urself n all and sundry ?hit me back.  & neutral\\
95 & cute outfit this is helena lol & positive\\
96 & Thanks Heather, It was a great day just being here, but the added bliss is my new orange couch. & positive\\
97 & hey jai'me, want to do something before you leave for la??? your profile picture is pretty enticing....and I NEED TO LEAVE THE HOUSE BEFORE I SHOOT SOMEBODY. i've barely been out for A WEEK. & negative\\
98 & thank you so much for becoming a fan of the over easy cafe i am trying to get 1000000 fans     this is where i work and no one thinks i can get that many fans so thank you again beautiful & positive\\
99 & I only have a t-shirt on and Peters friends over soooo...ur gonna hafta come get it!!! Ohhhh and btw...the battery is just about dead!!! & neutral\\
100 & We're looking forward to it too.  I did manage to find some time and the beard is gone.  I feel naked now. & positive\\
		\end{longtable}
		\end{footnotesize}
	\end{center}
% section sample_data (end)