\begin{titlepage} \raggedright
36 Queens College Dr\\
Richmond Hill, Ontario\\
L4B 1P2\newline

May 1, 2009\newline

Professor Manoj Sachdev, chair\\
Electrical and Computer Engineering\\
University of Waterloo\\
Waterloo, Ontario\\
N2L 3G1\newline

Dear Sir,\newline

This report, entitle ``Quantification of User Sentiment'', was prepared as my 3B Work Report for the Data Science Team of the Engineering division of Facebook Inc. This is in fulfillment of the course WKRPT400 and was written as an analysis of the work assigned to me during my work term by Roddy Lindsay. It is a confidential-1 report.\newline

Through headed by Chamath Palihapitiya - the VP of User Growth, Mobile and International Expansion - the Data Science team is part of the Engineering division of Facebook.  The Engineering division develops all new products and solutions for the company's main product, Facebook. This includes maintaining and updating current products, creating new products or developing a number internal applications. As a mainstream technology company, all aspects of the Engineering division are required to successfully maintain the daily operations of the company.\newline

The Data Science team - managed by Cameron Marlow - is primarily responsible for the development of methods and tools to organize, utilize, displaying and visualizing various data sets. These tools are used by various teams in understanding relevant data and using that data to achieve their goals and make defensible decisions. The final task for a Data Scientist is to aid other teams in understanding what data is relevant and how to utilize it.\newline

I would like to thank Mr.\ Roddy Lindsay for providing me with valuable advice in researching this topic.  I also with to thank Ms.\ Casey Song for proofreading this report and improving its appearance. I hereby confirm that I have received no further help in writing this report.  I also confirm that this report had not been previously been submitted for academic credit at this or any other academic institution.\newline
\vfill
Sincerely,\newline

Osman Currim, 20202897
\end{titlepage}