\begin{titlepage} \raggedright
36 Queens College Dr\\
Richmond Hill, Ontario\\
L4B 1P2\newline

August 11, 2008\newline

Professor Sujeet Chaudhuri, chair\\
Electrical and Computer Engineering\\
University of Waterloo\\
Waterloo, Ontario\\
N2L 3G1\newline

Dear Sir,\newline

This report, entitle ``Optimization and Elimination of Bottlenecks in kdb+'', was prepared as my 3A Work Report for the e-Trading Execution team (eT) of the Fixed Income IT division of Barclays Capital. This is my third work term report and was written as an analysis of the work assigned to me during my work term by Sonia Saldanha.\newline

The Fixed Income IT division provides IT infrastructure for all aspects of the Fixed Income division in Barclays Capital and is headed by Neil Chinai. This includes application development, testing, release and support, as well as maintaining the Trade Capture, Algorithmic Trading, Risk and Pricing systems.  Each of these separate teams work together to provide excellence and technological innovation - all of which is required to successfully maintain the daily operations of the Fixed Income trading and sales desks.\newline

The eT team - managed by Sonia Saldanha, my supervisor - is primarily responsible for development of the eT plugin system, that is the front end to all the systems that the Traders on the trading floor use.  They are also the owners of the kdb+ database system that I will be analyzing in this report.  kdb+ is used as the back-end system for many of the reporting and analysis tools.\newline

I would like to thank Ms.\ Sonia Saldanha, and Mr.\ Vivek Viswanathan for providing me with valuable advice in researching this topic.  I also with to thank Ms.\ Casey Song for proofreading this report and improving its appearance. I hereby confirm that I have received no further help in writing this report.  I also confirm that this report had not been previously been submitted for academic credit at this or any other academic institution.\newline
\vfill
Sincerely,\newline

Osman Currim, 20202897
\end{titlepage}