\section*{Summary} % (fold)
\label{sec:summary}
\addcontentsline{toc}{section}{Summary}

The main purpose of this report is to analyze certain bottlenecks and common errors within a kdb+ database environment in both the hardware and software layers.  Methods of removing these bottlenecks and errors will be discussed as well as the implementation of those methods.\newline
 
This report is intended for an audience with an intermediate knowledge of databases in the form of both hardware and software.\newline

The major points covered in this report are a selection of bottlenecks and common errors that can be found when using or developing for a kdb+ database system.  A description of each issue is provided along with specifics on how best to rectify these issues.  The advantages and disadvantages of applying these fixes as they pertain to efficiency and resource requirements are discussed.\newline

The major conclusions in this report are that it is feasible to apply these concepts and they will benefit a given kdb+ database system by minimizing hidden errors and maximizing efficiency.\newline

The major recommendations in this report are should a company be able to afford the initial costs of hardware, certain pieces should be purchased to maintain high integrity of the system.  One team member of any given team that uses a kdb+ system should go to seminars and other training sessions and then be assigned the task of checking kdb+ related software for hidden bugs and inefficiencies.  Lastly, at least one co-op student from an engineering program should be given the project of applying and testing these changes to a kdb+ system.
% section summary (end)