\begin{titlepage} \raggedright
36 Queens College Dr\\
Richmond Hill, Ontario\\
L4B 1P2\newline

January 5, 2008\newline

Professor Sujeet Chaudhuri, chair\\
Electrical and Computer Engineering\\
University of Waterloo\\
Waterloo, Ontario\\
N2L 3G1\newline

Dear Sir,\newline

This report, entitle ``Application of Continuous Integration Concepts in Workflow Automation'', was prepared as my 2B Work Report for the Global Technology and Operations (GTO) of Royal Bank of Canada (RBC). This is my second work term report and was written as an analysis of the work assigned to me during my work term by Juraj Liska and Douglas Acheson.\newline

GTO provides the IT infrastructure for RBC. This includes project execution, channel delivery, process excellence and technological innovation - all of which is required to successfully maintain the daily operations of major bank.\newline

The Common Components Centre of Excellence (CCCoE) department, in which I was employed, is headed by Jennifer Hong and managed by a number of Project Managers including Juraj Liska - my supervisor. CCCoE is primarily responsible for the design and development of a number of technology and channel neutral, reusable ``Common Components" that other departments in GTO utilize to create client-facing front-end software. This allows for quicker and more efficient integration as well as higher quality and easier maintainability of all the products GTO produces.\newline

I would like to thank Mr.\ Juraj Liska, Mr.\ Douglas Acheson, and Mr.\ Paul Cashmore for providing me with valuable advice in researching this topic.  I also with to thank Ms.\ Casey Song for proofreading and improving its appearance. I hereby confirm that I have received no further help in writing this report.  I also confirm that this report had not been previously been submitted for academic credit at this or any other academic institution.\newline
\vfill
Sincerely,\newline

Osman Currim, 20202897
\end{titlepage}