\section*{Summary} % (fold)
\label{sec:summary}
\addcontentsline{toc}{section}{Summary}

The main purpose of the report is to analyze certain key concepts of Continuous Integration, a software development methodology, and discuss how they apply to the automation of complex workflows in large projects.\newline
 
This report is intended for an audience with an intermediate knowledge of automation and programming methodologies and a basic knowledge of workflows.\newline

The major points covered in this report are a selection of relevant key concepts, or practices, of Continuous Integration that can be applied to workflow automation. A description of the concept is provided along with specifics on how the concept could be applied to workflow automation. The advantages and disadvantages of applying the concepts as they pertain to efficiency and resource requirements are discussed.\newline

The major conclusions in this report are that it is feasible to apply these concepts and that they do have significant advantages in increasing efficiency while decreasing the number of resources required.\newline

The major recommendations in this report are should a company be able to afford the initial costs of automating complex manual workflows and applying Continuous Integration concepts to increase efficiency, they should. Other software development methodologies should be inspected to see if there are other concepts that would aid in the development of automated workflows. Lastly, at least one co-op student from an engineering program should be given the project of actually applying and testing these concepts on some complex workflows.
% section summary (end)